Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-30 introduction.tex
move notebook stats to interview section

Over the past two \gordon{three?} years, we prototyped RCloud and deployed it to
a community of data scientists, business analysts and other colleagues.  The
platform today has over 300 active accounts; about 20 people use it regularly,
another 30 people use it more than once a week, and another 50 use it more than
once a month.  There are over 5000 notebooks, of which more than 500 have been
starred and more than 350 have been forked. \gordon{Is this the right place for
the notebook stats? We haven't defined forking or starring yet.}  Most of the
active users are members of AT\&T Labs, but some are data scientists and other
collaborators in other business units.

>>>>

Over the past two \gordon{three?} years, we prototyped RCloud and deployed it to
a community of data scientists, business analysts and other colleagues.  The
platform today has over 300 active accounts; about 20 people use it regularly,
another 30 people use it more than once a week, and another 50 use it more than
once a month.  Most of the
active users are members of AT\&T Labs, but some are data scientists and other
collaborators in other business units.
